Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density \thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-05-31 manuscript.tex
sec 4 updates

\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 6in]{FACULAE_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{\umberto{Set of spurious variations in RV's caused by a faculae using a Normal and a SN fit before and once corrected from stellar activity. The new correction is done using Eq.~\ref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}. Once corrected for stellar activity using the proposed linear function (black dots), the residuals present a smaller systematic component if compared with the residuals obtained with the usual correction (blue triangles).}}
    \label{fig:faculae.correction}
\end{center}
\end{figure*}

>>>>

\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 6in]{FACULAE_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{(top) The spurious RVs caused by a facula in the simulated data using a Normal and a SN fit.  before and once corrected from stellar activity. \jessi{What is the correction done here?  I think what you mean is this:  ``The black circles are the estimated RVs and the red plus signs are the estimated RVs from the fit model of  Eq.~\ref{eq:RV:correction}.''  If my assumption is correct, the legend should say ``RV estimates'' and ``RV model'' or something like that.  Otherwise this is rather confusing because in the bottom plot you are actually comparing residuals from two models, while the top has a different interpretation.}
   %
 (bottom) The residuals from the model fit using Eq.~\ref{eq:RV:correction} (new correction) and the usual correction \jessi{it might be helpful to actually have an equation for the usual/old model}.  The residuals have a smaller systematic component when using the proposed model of 
  Eq.~\ref{eq:RV:correction} (blue circles) compared to the usual model (blue triangles).
The estimated parameters are presented in Table \ref{table:faculae.test} \jessi{This table only has p-values and $R^2$}. }
    \label{fig:faculae.correction}
\end{center}
\end{figure*}
